
\subsection{Technology Stack} \

For this project, we adopted the \textbf{T3 Stack} \footcite{CreateT3App}, a modern full-stack framework designed to accelerate web application development with strong type safety and developer experience. The primary technologies we used are:


\begin{itemize}
	\item \textbf{Next.js} \footcite{NextjsVercelReact}:
	      A React-based framework that supports server-side rendering, static site generation, and API routes, enabling scalable and performant web applications.

	\item \textbf{NextAuth.js} \footcite{AuthjsAuthenticationWeb}:
	      A flexible authentication library integrated with Next.js, providing secure user login and session management with minimal setup.

	\item \textbf{Prisma} \footcite{PrismaInstantPostgres}:
	      A type-safe Object Relational Mapper (ORM) that simplifies database access and schema migrations while maintaining strong typing in Typescript.

	\item \textbf{Tailwind CSS} \footcite{TailwindCSSRapidly}:
	      A utility-first CSS framework that enables rapid UI development with consistent and responsive design patterns.

	\item \textbf{tRPC} \footcite{TRPCMoveFast2022}:
	      A type-safe API framework for building end-to-end type-checked procedures, fully integrated with React Query for efficient client-side data fetching and caching.

	\item \textbf{shadcn} \footcite{shadcnFoundationYourDesign}:
	      A collection of pre-built, customizable UI components that align with modern design practices and streamline interface development.

	\item \textbf{Vitest} \footcite{Vitest} \& \textbf{Cypress} \footcite{TestingFrameworksJavascript}:
	      Testing frameworks used for unit, integration, and end-to-end testing, ensuring code reliability and application correctness.
\end{itemize}

This stack was chosen because it balances rapid development with maintainability, strong type safety, and a vibrant ecosystem, making it well-suited for building scalable, production-ready applications. It also makes deploying with Vercel or Docker easy.

